### 2024-12-09 Draft1.tex
Finished the Encryption Section

For this exploration, I will be encrypting the message \( M = 45678 \) using a second-order non-homogeneous differential equation. The added complexity of a second-order equation models realistic challenges in encryption while showing the role of calculus.

To begin with the 1st key component mentioned in the \textit{Foundation of Calculus Cryptography} section, I will encrypt the message. I will be selecting the differential equation:
\[
\frac{d^2y}{dx^2} - 5\frac{dy}{dx} + 6y = f(x),
\]
where \( f(x) = 45678x^2 + 34125 \) encodes the message. The corresponding initial conditions are chosen as \( y(0) = 0 \) and \( y'(0) = M \), embedding \( M = 45678 \) as part of the solution.

@@

For the homogeneous equation:
\[
r^2 - 5r + 6 = 0,
\]
I solved the characteristic equation for roots as
\[
r = 2, \quad r = 3.
\]
As a result, the homogeneous solution is:
\[
y_h(x) = C_1e^{2x} + C_2e^{3x},
\]
in which \( C_1 \) and \( C_2 \) are constants that are determined by the initial conditions set above.

@@

@@

For the \textbf{particular solution}, I used the assumption that the form was \( y_p(x) = Ax^3 + Bx^2 + Cx + D \). By substituting \( y_p(x) \) and its derivatives into the original equation, I got
\[
\frac{d^2}{dx^2}(Ax^3 + Bx^2 + Cx + D) - 5\frac{d}{dx}(Ax^3 + Bx^2 + Cx + D) + 6(Ax^3 + Bx^2 + Cx + D) = 45678x^2 + 34125.
\]
\centering Expanding and equating coefficients of \( x^n \), I solved for \( A, B, C, \) and \( D \). The result was
\[
y_p(x) = 15226x^3 - 30452x^2 + 45678x + 34125.
\]

The general solution of this is:
\[
y(x) = C_1e^{2x} + C_2e^{3x} + 15226x^3 - 30452x^2 + 45678x + 34125.
\]

Next, I applied the initial conditions to determine the constants \( C_1 \) and \( C_2 \) and find the particular solution of the encrypted \( M \).

Using \( y(0) = 0 \) and \( y'(0) = M = 45678 \):
\begin{enumerate}
    \item Substitute \( y(0) = 0 \):
    \[
    C_1 + C_2 + 34125 = 0 \quad \Rightarrow \quad C_1 + C_2 = -34125.
    \]

    \item Compute \( y'(x) \):
    \[
    y'(x) = 2C_1e^{2x} + 3C_2e^{3x} + 45678 - 60904x + 45678x^2.
    \]
    Substitute \( y'(0) = 45678 \):
    \[
    2C_1 + 3C_2 + 45678 = 45678 \quad \Rightarrow \quad 2C_1 + 3C_2 = 0.
    \]

    \item Solve this system of equations:
    \[
    C_1 = -10237.5, \quad C_2 = -23887.5.
    \]
\end{enumerate}

Thus, the encrypted solution is:
\[
y(x) = -10237.5e^{2x} - 23887.5e^{3x} + 15226x^3 - 30452x^2 + 45678x + 34125.
\]

\subsubsection*{Transmission}
The encrypted function \( y(x) \) and the differential equation \( \frac{d^2y}{dx^2} - 5\frac{dy}{dx} + 6y = f(x) \) are transmitted to the recipient, along with the initial conditions.

\subsection*{Decryption Using Calculus Cryptography}

@@

\subsubsection*{Step 2: Recover the Message \( M \)}
The recipient identifies \( M \) directly from the initial condition \( y'(0) = M \). Thus, \( M = 45678 \).

>>>>

For this exploration, I will be encrypting the message \( M = 83495 \) using a second-order non-homogeneous differential equation. The added complexity of a second-order equation models realistic challenges in encryption while showing the role of calculus.

To begin with the 1st key component mentioned in the \textit{Foundation of Calculus Cryptography} section, I will encrypt the message. I will be selecting the differential equation:
\[
\frac{d^2y}{dx^2} - 5\frac{dy}{dx} + 6y = f(x),
\]
where \( f(x) = 45678x^2 + 34125 \), or the forcing function, encodes the message. Only the recipient and sender have access to the forcing function. The corresponding initial conditions are chosen as \( y(0) = M \) and \( y'(0) = 0 \). This ensures that \( M \) is embedded solely in the homogeneous solution, keeping the particular solution independent of \( M \).

@@

\vspace{0.1in}

For the homogeneous equation:
\[
r^2 - 5r + 6 = 0,
\]
I solved the characteristic equation for roots as
\[
r = 2, \quad r = 3.
\]
As a result, the homogeneous solution is:
\[
y_h(x) = C_1e^{2x} + C_2e^{3x},
\]
in which \( C_1 \) and \( C_2 \) are constants determined by the initial conditions set above.

@@

\vspace{0.1in}

@@

For the \textbf{particular solution}, I used the assumption that the form was \( y_p(x) = Ax^3 + Bx^2 + Cx + D \). By substituting \( y_p(x) \) and its derivatives into the original equation, I performed the following calculations:

\begin{enumerate}
    \item Compute derivatives of \( y_p(x) \):
    \[
    \frac{dy_p}{dx} = 3Ax^2 + 2Bx + C, \quad \frac{d^2y_p}{dx^2} = 6Ax + 2B
    \]

    \item Substitute into the original non-homogenous differential equation with \( f(x) = 45678x^2 + 34125 \) on the right-hand side:
    \[
    (6Ax + 2B) - 5(3Ax^2 + 2Bx + C) + 6(Ax^3 + Bx^2 + Cx + D) = 45678x^2 + 34125
    \]

    \item Group terms by powers of \( x \) and equate coefficients:
    \begin{itemize}
        \item Coefficient of \( x^3 \): \( 6A = 0 \quad \Rightarrow \quad A = 0. \)
        \item Coefficient of \( x^2 \): \( -15A + 6B = 45678 \quad \Rightarrow \quad B = 7613. \)
        \item Coefficient of \( x \): \( 6A - 10B + 6C = 0 \quad \Rightarrow \quad C = 12688.33. \)
        \item Constant term: \( 2B - 5C + 6D = 34125 \quad \Rightarrow \quad D = 13723.44. \)
    \end{itemize}
\end{enumerate}

Thus, the particular solution is:
\[
y_p(x) = 7613x^2 + 12688.33x + 13723.44
\]

The general solution with the initial conditions is:
\[
y(x) = C_1e^{2x} + C_2e^{3x} + 7613x^2 + 12688.33x + 13723.44
\]

% Applying Initial Conditions

Next, I applied the initial conditions \( y(0) = M \) and \( y'(0) = 0 \) to solve for \( C_1 \) and \( C_2 \):
\begin{enumerate}
    \item Substitute \( y(0) = M \):
    \[
    C_1 + C_2 + 13723.44 = M \quad \Rightarrow \quad C_1 + C_2 = M - 13723.44.
    \]

    \item Compute \( y'(x) \):
    \[
    y'(x) = 2C_1e^{2x} + 3C_2e^{3x} + 2(7613)x + 12688.33.
    \]
    Substitute \( y'(0) = 0 \):
    \[
    2C_1 + 3C_2 + 12688.33 = 0 \quad \Rightarrow \quad 2C_1 + 3C_2 = -12688.33.
    \]

    \item Solve this system of equations:
    \[
    \begin{aligned}
        & C_1 + C_2 = M - 13723.44, \\
        & 2C_1 + 3C_2 = -12688.33.
    \end{aligned}
    \]
    Solving these equations with \( M = 83495 \), I found:
    \[
    C_1 = 3M - 263903.21, \quad C_2 = -2M + 197131.77.
    \]
\end{enumerate}

As a result, the final encrypted solution is:
\[
y(x) = (3M - 263903.21)e^{2x} + (-2M + 197131.77)e^{3x} + 7613x^2 + 12688.33x + 13723.44.
\]

\subsubsection*{Transmission}

After encrypting the function, \( y(x) \) and the initial conditions are transmitted to the recipient. This ensures that the key, the forcing function \( f(x) \), and the encrypted message \( M \) are kept secure during transmission.

\subsubsection*{Decryption}

@@

After transmission and decryption, the recipient is able to correctly calculate \( M \) directly from the initial condition \( y'(0) = M \). As a result, \( y'(0) = M = 45678 \).
